---
title: 'Data Wrangling Exercise : Case Tagging'
author: "Yash Gupta"
date: "15/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Task-1:Perform Descriptive Analysys on Data
```{r}
data_tag = readxl::read_xlsx(path = "./sampleid.xlsx")

#No. of rows
nrow(data_tag)

#Names of coloumn
names(data_tag)

#Class of each coloumn 
sapply(data_tag,class)

#Total number of unique tickets
length(unique(data_tag$`( Case ID #)`))

#Range of numeric coloumn
range(data_tag$`Reassignment count`,na.rm = T)

#No. of counts and proportion each levels in factor and numeric coloumn
table(data_tag$`Reassignment count`)
prop.table(table(data_tag$`Reassignment count`))
table(data_tag$`Assignment Group`)
prop.table(table(data_tag$`Assignment Group`))

#Frecquency of each tickets
library(dplyr)
data_tag %>% group_by(`( Case ID #)`) %>% summarise(frequency = n())
```

Task-2:Clean the Headers (i.e. remove special characters) and replace the space with “_” (underscore) using DPLYR and otherwise

```{r}
    library(janitor)
    data_tag = data_tag %>% clean_names(case = "parsed")
    data_tag
```

 Task-3 : A Case ID can be created/Opened by anyone (Imarticus or Non-Imarticus). But in subsequent entries if its assigned to Non-Imarticus (blank cells) even once then the particular Case ID should belong to Non-Imarticus else it should belong to Imarticus.
```{r}
data_tag %>%
    group_by(Case_ID_number)%>%
        summarise(Tag=ifelse(n()==1|(n()-1)==length(which(Assignment_Group!=""&row_number()!=1)),"Imarticus","Non-Imarticus"))
```






























